Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-05 documentation/paper.tex
Added wall event positions graph
Added graph for waveform grid search
Clarified lack of decisiveness

@@

A convolutional neural network was used for analyzing the raw waveform $\omega$ directly, without any preprocessing whatsoever. This avoids any destruction of information, and should be possible, in theory, for a neural network to handle. For this task, a very deep 1-dimensional fully convolutional neural network was applied. The architecture was inspired by the M34-res network \cite{verydeepconvnets} for analysis of raw waveforms. L2 regularization was used to alleviate overfitting, and batch normalization was applied to the input. (Its hyperparameters were modified significantly through manual empirical testing as well as grid searches.)

@@

Once the audio was cropped properly, $DeepConv(\omega)$ achieved a maximum of 77\% accuracy on validation data. Using the same network architecture (except for the input layer), $DeepConvWithPos(\omega, \chi)$ managed 85\%. The maximum obtained on a grid search with position correction was 91\%. While this is not a drastic improvement, it is a fairly strong indication that the network is able to extract meaningful information from the position, which may be used in an internal position correction of the volume. That said, neither of these accuracy statistics are particularly good (graphs of 85\% accuracy often appear effectively random), which does not bode well for this input format as a whole.

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=\textwidth]{wall_event_positions}
    \caption{\label{} A visualization of the fiducial cuts and how they match up with the pressure and acoustic cuts.}
\end{figure}

@@

A convolutional neural network was used for analyzing the raw waveform $\omega$ directly, without any preprocessing whatsoever, and without application of $WallCut(D)$. This avoids any destruction of information, and should be possible, in theory, for a neural network to handle. For this task, a very deep 1-dimensional fully convolutional neural network was applied. The architecture was inspired by the M34-res network \cite{verydeepconvnets} for analysis of raw waveforms. L2 regularization was used to alleviate overfitting, and batch normalization was applied to the input. (Its hyperparameters were modified significantly through manual empirical testing as well as grid searches.)

@@

Once the audio was cropped properly, $DeepConv(\omega)$ achieved a maximum of 77\% accuracy on validation data. Using the same network architecture (except for the input layer), $DeepConvWithPos(\omega, \chi)$ managed 85\%. The maximum obtained on a grid search with position correction was 91\%. While this is not a drastic improvement, it is a fairly strong indication that the network is able to extract meaningful information from the position, which may be used in an internal position correction of the volume.

It is difficult to say with a high degree of confidence whether or not this is an effective discriminator, since Acoustic Parameter is not decisive on data without $WallCut(D)$. However, the lack of decisiveness observed even when accuracy was relatively high, as seen in Figure \ref{waveform_best_validation}, implies this is a suboptimal technique.

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{waveform_best_validation}
    \caption{\label{waveform_best_validation} Accuracy of $DeepConvWithPos(\omega, \chi)$ compared to Acoustic Parameter at discriminating between run types without $WallCut(D)$ (91\% accuracy).}
\end{figure}
